### 2021-04-21 paper/ase21/analyzer.tex
Revised Sec. 3
[ASE21] Updated citation for report

We define a denotational semantics of the modified $\ires$ for instructions
$\semi{\inst}: \dom \rightarrow \dom$, references $\semr{\refer}: \dom
\rightarrow \valset$, and expressions $\seme{\expr}: \dom \rightarrow \valset$
where $\dom$ and $\valset$ denote states and values, respectively.
For brevity, we omit it in this paper and refer the
interested readers to a companion report~\inred{\cite{report}}.

@@

We now define the abstract semantics of instructions $\asemi{\inst}$ in Figure~\ref{fig:abs-sem}
and the abstract semantics of references $\asemr{\refer}$
and expressions $\aseme{\expr}$ in a companion report~\inred{\cite{report}}.
To avoid the explosion of type-sensitive
views, we upcast the argument type before function calls with the
following function:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \resizebox{0.8\columnwidth}{!}{$
    \upcast(\ty) = \left\{
      \begin{array}{ll}
        \tnormal(\upcast(\ty')) & \text{if} \; \ty = \tnormal(\ty')\\
        \clist{\upcast(\ty')} & \text{if} \; \ty = \clist{\ty'}\\
        \tstr & \text{if} \; \ty = \str\\
        \tbool & \text{if} \; \ty = \bool\\
        \ty & \text{otherwise}\\
      \end{array}
    \right.
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
and $\upcasts$ denotes a point-wise extension of $\upcast$ for type sequences.
For branches and assertions, we use the following $\pass$ function to prevent
infeasible control flows:

>>>>

We define a denotational semantics of the modified $\ires$ for instructions
$\semi{\inst}: \dom \rightarrow \dom$, references $\semr{\refer}: \dom
\rightarrow \valset$, and expressions $\seme{\expr}: \dom \rightarrow \valset$
where $\dom$ and $\valset$ denote states and values, respectively.
For brevity, we omit it in this paper and refer the
interested readers to a companion report~\cite{report}.

@@

We now define the abstract semantics of instructions $\asemi{\inst}$ in Figure~\ref{fig:abs-sem}
and the abstract semantics of references $\asemr{\refer}$
and expressions $\aseme{\expr}$ in a companion report~\cite{report}.
To avoid the explosion of type-sensitive
views, we upcast the argument type before function calls with the
following function:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \resizebox{0.8\columnwidth}{!}{$
    \upcast(\ty) = \left\{
      \begin{array}{ll}
        \tnormal(\upcast(\ty')) & \text{if} \; \ty = \tnormal(\ty')\\
        \clist{\upcast(\ty')} & \text{if} \; \ty = \clist{\ty'}\\
        \tstr & \text{if} \; \ty = \str\\
        \tbool & \text{if} \; \ty = \bool\\
        \ty & \text{otherwise}\\
      \end{array}
    \right.
  $}
  \vspace*{-0.5em}
\end{figure} \noindent
and $\upcasts$ denotes a point-wise extension of $\upcast$ for type sequences.
For branches and assertions, we use the following $\pass$ function to prevent
infeasible control flows:
